\section{Nash's Theorem}
	We prove that every finite game has a Nash Equilibrium by drawing together
	two seemingly unrelated things.

	\subsection{Sperner's Lemma}
	Consider the graph formed from the triangulation of a triangle -- that is,
	a graph that is made up only of smaller triangles.

	\begin{definition}[Valid colouring]
		A valid colouring is a colouring of the vertices, each with a colour in
		the set $\{R,G,B\}$, such that:
		\begin{itemize}
			\item each of the three corners is a distinct colour
			\item no vertex on the side of the big triangle has the same colour
				as the opposite corner
		\end{itemize}
	\end{definition}

	We call a triangle \textit{panchromatic} if each of its vertices have a
	unique colour. We will now state Sperner's Lemma and prove it in two
	different ways.

	\begin{theorem}[Sperner's Lemma]
		Every valid colouring has an odd number of panchromatic triangles.
	\end{theorem}

	\begin{proof}[Proof 1 \emph{(by counting RB triangles)}]
		Let:
		\begin{itemize}
			\item $\bigtriangleup^{RGB} :=$ number of RGB triangles
			\item $\bigtriangleup^{RB} :=$ number of RB triangles
			\item $|^{RB}_X :=$ number of external RB edges, $|^{RB}_I :=$
				number of internal RB edges
		\end{itemize}

		By an external edge, we mean an edge that was formed directly from the
		original triangle, and an internal edge is every edge contained inside
		the triangulation.

		\begin{claim*}
			$|^{RB}_X$ is odd.
		\end{claim*}
		\begin{subproof}
			Consider two corners of the large triangle, where the first is
			coloured red, and the other blue. Since we have a valid colouring,
			no vertex along the edges joining these two corners is coloured
			green, so we only have RB, RR, or BB edges. We get a new RB edge
			whenever we change colour. Since the colours of the corners are
			different, we must change colour an odd number of times, so the
			number of RB edges on the exterior is odd.
		\end{subproof}

		\begin{claim*}
			Each RGB triangle has one RB edge. Each RB triangle has two RB
			edges. All other triangles have 0 RB edges.
		\end{claim*}

		\begin{claim*}
			$\bigtriangleup^{RGB} + 2\bigtriangleup^{RB} = |^{RB}_X +
			2|^{RB}_I$
		\end{claim*}
		\begin{subproof}
			The number of RB edges is equal to
			$\bigtriangleup^{RGB}+2\bigtriangleup^{RB}$. This counts all
			the interior RB edges twice, as each internal edge separates two
			triangles, and each external RB edge once, as exactly one triangle
			touches it.
		\end{subproof}

		Hence $\bigtriangleup^{RGB} = |^{RB}_X + 2|^{RB}_I -
		2\bigtriangleup^{RB} = 2(|^{RB}_I - \bigtriangleup^{RB}) +
		|^{RB}_X$, which is odd.
	\end{proof}

	\begin{proof}[Proof 2 \emph{(by following the End-of-a-Line)}]
		Construct a directed graph based on the triangulation as follows:
		\begin{itemize}
			\item add edges from the B corner to all vertices on the RB side
			\item create a node for each cell (internal triangle), and one for
				the ``outside'' edge
			\item create a directed arc across every RB edge, where R is ``to
				the left'' as we traverse the arc)
		\end{itemize}

		Every node has in-degree at most one and out-degree at most one. Thus
		the graph consists only of isolated vertices, edge-disjoint paths, and
		edge-disjoint cycles. By the Handshaking Lemma, the number of nodes of
		degree exactly one is even. Nodes with degree exactly one appear 
		in panchromatic triangles (one way in, no way out), and only RGB
		triangles contain these nodes of degree exactly one. We began by
		creating an artificial node outside of the large triangle -- every
		other node of degree one corresponds to a panchromatic triangle. Hence
		the number of nodes of degree exactly one in the original graph is odd,
		so the number of RGB triangles in the original graph is odd.
	\end{proof}

	\subsection{Brouwer's Fixed Point Theorem}
	A $k$-simplex is a $k$-dimensional polytope that is the convex hull of its
	$k+1$ vertices. The standard simplex that we will make use of is a simplex
	formed from $k+1$ standard unit vectors:
	\begin{equation}
		S^d = \{ (x_1, \ldots, x_{d+1}) \, | \, x_1 + \ldots + x_{d+1} = 1, x_i
		\ge 0 \text{ for } i = 1, \ldots, d+1 \}
	\end{equation}

	A set is compact if it is \textit{closed} -- it contains all its limit
	points -- and \textit{bounded} -- all its points lie within some fixed
	distance from one another.

	A convex set is a set of points such that, given any two points in the set,
	the line joining them lies entirely within that set.

	A fixed point of a function $f: A \rightarrow B$ is an element of the
	function's domain that maps to itself, that is, $c \in A$ is a fixed point
	of $f$ if $f(c) = c$.

	\begin{theorem}[Brouwer's Fixed Point Theorem]
		If $f: S \rightarrow S$ is a continuous function from a compact convex
		set to itself, then $f$ has a fixed point.
	\end{theorem}

	\begin{proof}[Proof \emph{(for d=1)}]
		$S^1$ is the unit interval. Let $f:[0,1] \rightarrow [0,1]$ be a
		continuous function. If $f(0)=0$ or $f(1)=1$ then we have found our
		fixed point. Otherwise, we have $f(0)>0$ and $f(1)<1$. The function
		$g(x) := x - f(x)$ is continuous, and $g(0)<0$ and $g(1)>0$. By the
		Intermediate Value Theorem, there must be some $x \in [0,1]$ for which
		$g(x) = 0$. Hence $x = f(x)$.
	\end{proof}

	\begin{proof}[Proof \emph{(for d=2)}]
		The function $f$ sends point $(\alpha, \beta, \gamma)$ to another point
		in the triangle: $f(\alpha, \beta, \gamma) = (\conj{\alpha},
		\conj{\beta}, \conj{\gamma})$. We begin the proof by defining a valid
		colouring of $S^2$ based on $f$:
		\begin{itemize}
			\item R if $\alpha > \conj{\alpha}$
			\item B if $\alpha \le \conj{\alpha}$ and $\beta > \conj{\beta}$
			\item G if $\alpha \le \conj{\alpha}$ and $\beta \le \conj{\beta}$
				and $\gamma < \conj{\gamma}$
		\end{itemize}

		\begin{fact}
			If a point has no colour, then it is a fixed point.
		\end{fact}

		\begin{claim*}
			The colouring is valid.
		\end{claim*}
		\begin{subproof}
			Recall that a colouring is valid if each of the three vertices of a
			triangle receives a different colour and no point on the side is
			assigned the colour equal to the colour on the opposite corner. The
			colours of the points $(1,0,0), (0,1,0),$ and $(0,0,1)$ are R, B,
			and G respectively. Furthermore,
			\begin{itemize}
				\item no point on the $(1,0,0)-(0,1,0)$ edge has colour G
				\item no point on the $(0,0,1)-(1,0,0)$ edge has colour B
				\item no point on the $(0,1,0)-(0,0,1)$ edge has colour R
			\end{itemize}
		\end{subproof}

		We then use Sperner's Lemma and the compactness of $S^2$ to find a
		fixed point. Let $T_1, T_2, \ldots$ be triangulations of $S^2$ such
		that the largest diameter of the cells converges to 0. By Sperner's
		Lemma, every $T_i$ has a panchromatic cell with corners:
		\begin{itemize}
			\item $x_i = (\alpha_i, \beta_i, \gamma_i)$ with colour R
			\item $x_i' = (\alpha_i', \beta_i', \gamma_i')$ with colour B
			\item $x_i'' = (\alpha_i'', \beta_i'', \gamma_i'')$ with colour G
		\end{itemize}

		In other words, assuming that we have:
		\begin{equation}
			\begin{split}
				f(x_i) & = (\conj{\alpha}_i, \conj{\beta}_i, \conj{\gamma}_i) \\
				f(x_i') & = (\conj{\alpha}_i', \conj{\beta}_i', \conj{\gamma}_i') \\
				f(x_i'') & = (\conj{\alpha}_i'', \conj{\beta}_i'', \conj{\gamma}_i'')
			\end{split}
		\end{equation}

		Then:
		\begin{equation}
			\label{eq:fixedPoints}
			\begin{split}
				\alpha_i > \conj{\alpha}_i & \text{ (as $x_i$ is R)} \\
				\beta_i' > \conj{\beta}_i' & \text{ (as $x_i'$ is B)} \\
				\gamma_i'' > \conj{\gamma}_i'' & \text{ (as $x_i''$ is G)}
			\end{split}
		\end{equation}

		Since $S^2$ is a compact (closed and bounded) subset of $\mathbb{R}^3$,
		by the Bolzano-Weierstrass Theorem\footnote{Each bounded sequence in
		$\mathbb{R}^n$ has a convergent subsequence.}, there is a sequence $i_1
		< i_2 < \ldots$ such that $\lim_{k \rightarrow \infty} x_{i_k}$ exists
		(the sequence $\langle x_{i_k} \rangle$ converges).

		Since the diameters of the cells in triangulations $T_{i_1}, T_{i_2},
		\ldots$ converges to 0, we have $\lim_{k \rightarrow \infty} x_{i_k} =
		\lim_{k \rightarrow \infty} x_{i_k}' = \lim_{k \rightarrow \infty}
		x_{i_k}''$. Let $z = (\alpha, \beta, \gamma)$ and $f(z) =
		(\conj{\alpha}, \conj{\beta}, \conj{\gamma})$.
		Using~\eqref{eq:fixedPoints}, we have $\alpha \ge \conj{\alpha}, \beta
		\ge \conj{\beta}, \gamma \ge \conj{\gamma}$. Thus it follows that
		$\alpha = \conj{\alpha}, \beta = \conj{\beta}, \gamma = \conj{\gamma}$
		since $\alpha + \beta + \gamma = 1$ and $\conj{\alpha} + \conj{\beta} +
		\conj{\gamma}$, so we have $f(z) = z$, a fixed point.
	\end{proof}

	\begin{claim}
		Brouwer's Theorem can be proved for $d \ge 3$ by induction.
	\end{claim}
	\begin{remark}
		Brouwer's Fixed Point Theorem holds for continuous functions $f:C
		\rightarrow C$ where $C$ is convex and compact. Any convex compact set
		can be continuously deformed into $S^d$ for some $d$.
	\end{remark}

	\subsection{Nash's Theorem}
	We now prove the big Nash's Theorem for two players by bringing together
	the previous two results. The proof for $n$ players is a straightforward
	generalisation. Note that by a finite game, we mean a game in which there
	is a finite number of players each with a finite number of pure strategies.

	\begin{theorem}[Nash, 1951]
		Every finite game has a Nash Equilibrium.
	\end{theorem}
	\begin{proof}[Proof of Nash's Theorem]
		Player I has payoff matrix $\vect{A}$ and plays mixed strategy
		$\vect{x} \in \Delta^{m_1}$, while player II has payoff matrix
		$\vect{B}$ and plays mixed strategy $\vect{y} \in \Delta^{m_2}$.

		Let $k_i(x,y)$ denote player I's gain in utility from switching to
		strategy $i \in S_\text{I}$, and $k_j'(x,y)$ denote player II's gain in
		utility from switching to strategy $j \in S_\text{II}$:
		\begin{equation}
			\begin{split}
				k_i(x,y) & := \max \{ 0, (\vect{Ay})_i - \vect{x^\top A y} \} \\
				k_j'(x,y) & := \max \{ 0, (\vect{x^\top B})_j - \vect{x^\top A y} \} \\
			\end{split}
		\end{equation}

		We are at a Nash Equilibrium when $k_i(x,y) = k_j'(x,y)$ for some
		strategies $i \in S_\text{I}, j \in S_\text{II}$. Define the following
		mixed strategy for player I:
		\begin{equation}
			g(x,y) := \frac{1}{1 + \sum_{i \in [m_1]} k_i(x,y)} \begin{pmatrix}
				x_1 + k_1(x,y) \\
				\vdots \\
				x_{m_1} + k_{m_1}(x,y)
			\end{pmatrix}
		\end{equation}

		And the same for player II:
		\begin{equation}
			h(x,y) := \frac{1}{1 + \sum_{j \in [m_2]} k_j'(x,y)} \begin{pmatrix}
				x_1 + k_1'(x,y) \\
				\vdots \\
				x_{m_2} + k_{m_2}'(x,y)
			\end{pmatrix}
		\end{equation}

		\begin{claim*}
			$g(x,y)$ and $h(x,y)$ are valid mixed strategies.
		\end{claim*}
		\begin{subproof}
			We will prove for $g(x,y)$, and the same reasoning applies for
			$h(x,y)$.  Let $\conj{x} := \begin{pmatrix}
				x_1 + k_1(x,y) \\
				\vdots \\
				x_{m_1} + k_{m_1}(x,y) \\
			\end{pmatrix}$. In a valid mixed strategy the sum of entries must
			be equal to 1. We have:
			\begin{equation*}
				\begin{split}
					\sum_i \conj{x}_i & = \sum_i (x_i + k_i(x,y)) = \sum_i x_i +
					\sum_i k_i(x,y) \\
					& = 1 + \sum_i k_i(x,y)
				\end{split}
			\end{equation*}

			Hence, $\frac{1}{1 + \sum_i k_i(x,y)} \sum_i \conj{x}_i = 1$ and
			each $\conj{x}_i \ge 0$, since $k_i(x,y) \ge 0$ by definition.
		\end{subproof}

		Now define the continuous function $f:\Delta^{m_1} \times
		\Delta^{m_2} \rightarrow \Delta^{m_1} \times \Delta^{m_2}$ as
		follows:
		\begin{equation}
			f(x,y) = (g(x,y), h(x,y))
		\end{equation}

		Since $\Delta^{m_1} \times \Delta^{m_2}$ is a convex compact set,
		Brouwer's Theorem implies that $f$ has a fixed point. That is, there is
		an $x^* \in \Delta^{m_1}$ and a $y^* \in \Delta^{m_2}$ such that
		$f(x^*,y^*) = (x^*,y^*)$. Now we just need to show that $(x^*,y^*)$ is
		a Nash Equilibrium.

		\begin{claim*}
			$(x^*, y^*)$ is a Nash Equilibrium.
		\end{claim*}
		\begin{subproof}
			We must show that for all $i \in [m_1], j \in [m_2], k_i(x^*,y^*) =
			k_j'(x^*,y^*) = 0$. Assume there is an $i \in [m_1]$ such that
			$k_i(x^*,y^*) > 0$. Then there must be a $j \in [m_1]$ such that
			$x_j \neq 0$ and $k_j(x^*, y^*) = 0$. If we suppose that this is
			not true (i.e. that every $k_j(x^*,y^*) > 0$), then we have:
			\begin{equation*}
				\vect{x^\top A y} = \sum_{\ell \in [m_1]} x_\ell
				(\vect{Ay})_\ell > \sum_{\ell \in [m_1]} x_\ell (\vect{x^\top A
				y}) = \vect{x^\top A y} \sum_{\ell \in [m_1]} x_\ell =
				\vect{x^\top A y}
			\end{equation*}

			A contradiction.
		\end{subproof}

		Since $(x^*,y^*)$ is a fixed point of $f$, $g(x^*,y^*) = x^*$.
		Therefore,
		\begin{equation*}
			\frac{x^*_i + k_i(x^*, y^*)}{1 + \sum_{\ell \in [m_1]} k_\ell (x^*,
		y^*)} = x^* \qquad (\neq 0 \text{ as $x^*_i + k_i(x^*, y^*) \neq 0$})
		\end{equation*}

		Rearranging, we have $\sum_{\ell \in [m_1]} k_l(x^*, y^*) =
		\dfrac{k_i(x^*, y^*)}{x^*_i} > 0$, but then:
		\begin{equation*}
			\begin{split}
				\frac{x^*_j + k_j(x^*,y^*)}{1 + \sum_{\ell \in [m_1]} k_\ell
				(x^*, y^*)} & = \frac{x^*_j}{1 + \sum_{\ell \in [m_1]} k_\ell
				(x^*, y^*)} \\
				& = \frac{x^*_j}{1 + k_i(x^*,y^*) / x^*_i} \neq x^*_j
			\end{split}
		\end{equation*}

		This contradicts the fact that $(x^*,y^*)$ is a fixed point, and hence
		there is no $i$ such that $k_i(x^*, y^*) = 0$. Similar reasoning shows
		that $k_j'(x^*,y^*) = 0$ for all $j \in [m_2]$. Therefore no player can
		improve their expected payoff by switching strategy, so no player the
		incentive to unilaterally deviate. Thus $(x^*,y^*)$ is a Nash
		Equilibrium.
	\end{proof}
